---
title: "concept-norm-metrics"
output: html_document
---

# This is the analysis page of the MRNGO mini-norm (for DUCOG 2025)

## MISC
Let's read in the packages

```{r}
# PACAKAGES
library(dplyr)
library(tidyverse)
library(WordListsAnalytics)
library(readxl)
library(ggplot2)

theme_set(theme_light())

custom_theme = theme(
      plot.title = element_text(color="black", size=30, face="bold",  hjust = 0.5, vjust = 3), #30 for covariate plots
      axis.text.x = element_text(vjust = 0.5, hjust=0.5, size = 20, face="bold"), #was 16 for other plots besides rec resp rate
      axis.text.y = element_text(vjust = 0.5, hjust=0.5, size = 20, face="bold"),
      axis.title.x = element_text(vjust = -2, hjust=0.5, size = 26, face="bold"),
      axis.title.y = element_text(vjust = 3, hjust=0.5, size = 26, face="bold"),
      legend.text = element_text(vjust = 0.5, hjust=0.5, size = 22, face="bold"),
      legend.title = element_text(vjust = 0.5, hjust=0.5, size = 24, face="bold"),
      strip.text = element_text(vjust = 0.5, hjust=0.5, size = 22, face="bold"),
      panel.border = element_blank(),
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      plot.margin = margin(30, 30, 30, 30)
      )

```
RENAMING HUNGARIAN TO ENGLISH

```{r}
category_map <- list(
  cat_01 = "animals",
  cat_02 = "bodyparts",
  cat_03 = "clothes",
  cat_04 = "fooddrink",
  cat_05 = "locations",
  cat_06 = "people",
  cat_07 = "plants",
  cat_08 = "tools",
  cat_09 = "toys",
  cat_10 = "vehicles"
)

concept_map <- list(
  alma        = "apple",
  asztal      = "table",
  autó        = "car",
  bab         = "bean",
  ceruza      = "pencil",
  cipő        = "shoe",
  citrom      = "lemon",
  eper        = "strawberry",
  erdő        = "forest",
  gomba       = "mushroom",
  gyerek      = "child",
  helikopter  = "helicopter",
  hercegnő    = "princess",
  játszótér   = "playground",
  kacsa       = "duck",
  kard        = "sword",
  krumpli     = "potato",
  kutya       = "dog",
  kéz         = "hand",
  könyv       = "book",
  láb         = "leg",
  ló          = "horse",
  nadrág      = "trousers",
  nappali     = "livingroom",
  pulóver     = "sweater",
  seprű       = "broom",
  szem        = "eye",
  szőnyeg     = "carpet",
  tűzoltó     = "firefighter",
  vonat       = "train"
)

translations = c(
  "HOL_BOLT"   = "IN_STORE",      # old = new
  "LEHET_ESZIK" = "BE_EAT",
  "ILYEN_NAGY"       = "IS_BIG",
  "RÉSZE_LÁB"       = "HAS_LEG",
  "ILYEN_BARNA"       = "IS_BROWN",
  "HOL_HÁZ"       = "IN_HOUSE",
  "MIBŐL_FÉM"       = "MATERIAL_METAL",
  "ILYEN_PIROS"       = "IS_RED",
  "FAJTA_GYÜMÖLCS"       = "TYPE_FRUIT",
  "FAJTA_ÁLLAT"   = "TYPE_ANIMAL"
  # … and so on for all your feature names …
)

```

## READ-IN MRNGO DATA

READING IN DATA AND CLEANING

```{r}
mrngo_data = read_excel("../processed/MRNGO_manual_vector_lemmas_summary.xlsx",
                 sheet = "aggregated_data")

mrngo_data_cleaned = mrngo_data %>% 
  mutate(sex=as.factor(sex)) %>% 
  mutate(grade=as.factor(grade)) %>% 
  mutate(category = recode(category, !!!category_map),
         concept  = recode(concept,  !!!concept_map)
  ) %>% 
  mutate(category=as.factor(category)) %>% 
  mutate(concept=as.factor(concept)) %>% 
  mutate(
    age = if_else(age %in% c(0, 24), 
                  6L,    # ha egész számot akarsz
                  age)
  ) %>% 
  rename(feature = vector_lemma_C) %>% 
  mutate(feature = as.factor(feature)) %>% 
  distinct(ID, concept, feature, .keep_all = TRUE)

  
  
```

### CALCULATE MCRAE THINGS

```{r}

library(dplyr)
library(stringr)

# ── 0) First tally up your “production frequencies”  ────────────────────────────
df_counts <- mrngo_data_cleaned %>%
  count(concept, feature, name = "Prod_Freq")


# ── 1) Feature‐level summaries ──────────────────────────────────────────────────
feature_stats <- df_counts %>%
  group_by(feature) %>%
  summarise(
    Sum_PF_No_Tax = sum(Prod_Freq),       # total uses of that feature
    CPF            = n_distinct(concept)  # number of concepts in which it occurs
  ) %>%
  mutate(
    Disting  = if_else(CPF <= 2, "D", "ND"),
    Distinct = 1 / CPF                    # inverse of number of concepts
  )


# ── 2) Bring those back to the concept×feature table & compute CV ─────────────
df_pf <- df_counts %>%
  left_join(feature_stats, by = "feature") %>%
  mutate(
    CV_No_Tax = Prod_Freq / Sum_PF_No_Tax
  )


# ── 3) Within‐concept rankings & some string‐lengths ────────────────────────────
df_pf <- df_pf %>%
  group_by(concept) %>%
  arrange(desc(Prod_Freq)) %>%
  mutate(
    Rank_PF = row_number()
  ) %>%
  ungroup() %>%
  mutate(
    Feat_Length_Including_Spaces = str_length(feature),
    Length_Letters             = str_length(str_remove_all(concept, "[^A-Za-z]")),
    Length_Syllables           = str_count(concept, "[AEIOUYaeiouy]+"),
    Length_Phonemes            = NA_integer_  # ← you’ll need a phoneme counter/dictionary
  )


# ── 4) Concept‐level aggregates ──────────────────────────────────────────────────
concept_summary <- df_pf %>%
  group_by(concept) %>%
  summarise(
    Num_Feats_Tax         = n(),
    Num_Disting_Feats_Tax = sum(Disting == "D"),
    Disting_Feats._Tax    = Num_Disting_Feats_Tax / Num_Feats_Tax,
    Mean_Distinct_Tax     = mean(Distinct)
  )

# ── 6) Stitch everything back together ───────────────────────────────────────────
mrngo_data_clened_metrics <- df_pf %>%
  left_join(concept_summary, by = "concept")


# df_final now has one row per (concept, feature) with these new columns:
#   Rank_PF,  Sum_PF_No_Tax, CPF, Disting, Distinct,
#   CV_No_Tax, Feat_Length_Including_Spaces,
#   Length_Letters, Length_Phonemes, Length_Syllables,
#   Num_Feats_Tax, Num_Disting_Feats_Tax, Disting_Feats._Tax,
#   Mean_Distinct_Tax, Num_Corred_Pairs_No_Tax,
#   %_Corred_Pairs_Tax, Density_Tax


```

### SEMANTIC RICHNESS

```{r}
library(stringi)

# 1) read in the richness file
richness <- read_csv("../processed/MRNGO_mini-norm_richness.csv", col_types = cols())

# 3) build a little lookup table that also has a 'de-accented' key
map_df <- tibble(
  concept_hu   = names(concept_map),
  concept_de   = stringi::stri_trans_general(concept_hu, "Latin-ASCII"),
  concept_en   = unname(concept_map)
)

# 4) attach English names into richness
richness2 <- richness %>%
  # assume your CSV has a column called "concept" with NO accents
  mutate(concept_de = tolower(Concept)) %>%
  left_join(map_df, by = "concept_de") %>% 
  mutate(concept_en = as.factor(as.character(concept_en)))

# 5) now merge with your metrics (which already use English names in `concept`)
mrngo_data_clened_metrics_richness <- mrngo_data_clened_metrics %>%
  left_join(
    richness2 %>% select(concept_en, everything()), 
    by = c("concept" = "concept_en")
  )

# check
glimpse(mrngo_data_clened_metrics_richness)



```

### CONCEPT DATA

```{r}


# 1) Read your lookup sheet (first sheet by default; change sheet= if needed)
concept_info <- read_excel("../processed/MRNGO_concepts.xlsx", sheet = 1) %>%
  # keep only the three columns you need
  select(item_en, natural, word_frequency, aoa_any) %>%
  # make sure item_en is a character vector
  mutate(item_en = factor(item_en))
  
# 3) Left-join
mrngo_data_clened_metrics_richness <- mrngo_data_clened_metrics_richness %>%
  left_join(concept_info,
            by = c("concept" = "item_en"))  %>% 
  select(-Concept) %>% 
  rename(Concept=concept) %>% 
  rename(Feature=feature) 

# 4) Quick check
glimpse(mrngo_data_clened_metrics_richness)


```


## READ-IN MCRAE DATA
```{r}
mcrae_data = read_excel("../others/McRae-norm_filtered.xlsx",
                 sheet = "features")
mcrae_data_cleaned = mcrae_data %>% 
  mutate(Concept=as.factor(Concept)) %>% 
  mutate(Feature=as.factor(Feature)) %>% 
  mutate(WB_Label=as.factor(WB_Label)) %>% 
  mutate(WB_Maj=as.factor(WB_Maj)) %>%
  mutate(WB_Min=as.factor(WB_Min)) %>% 
  mutate(Disting=as.factor(Disting)) %>% 
  mutate(`Disting_Feats_%_No_Tax`=as.numeric(`Disting_Feats_%_No_Tax`)) %>% 
  mutate(Density_No_Tax=as.numeric(Density_No_Tax))
  



```
## READ-IN KREMER_IT
```{r}
kremer_it_data = read_excel("../others/Kremer_norm_filtered-IT.xlsx",
                 sheet = "frequency")
cols_to_convert <- c("Nationality", "Concept(EN)", "ConceptClass", "Concept(IT)", "Feature", "RelationType", "(Non)Distinguishing")

kremer_it_data_cleaned = kremer_it_data %>% 
  mutate(across(all_of(cols_to_convert), as.factor))

kremer_de_data = read_excel("../others/Kremer_norm_filtered-DE.xlsx",
                 sheet = "frequency")
cols_to_convert <- c("Nationality", "Concept(EN)", "ConceptClass", "Concept(IT)", "Feature", "RelationType", "(Non)Distinguishing")

kremer_de_data_cleaned = kremer_de_data %>% 
  mutate(across(all_of(cols_to_convert), as.factor))
```

## READ-IN VINSON
```{r}
vinson_data_features = read_excel("../others/Vinson-norm_filtered.xlsx",
                 sheet = "features")
vinson_data_richness = read_excel("../others/Vinson-norm_filtered.xlsx",
                 sheet = "richness")

vinson_merged_data <- merge(vinson_data_features, vinson_data_richness, by = "Concept", all = TRUE) %>% 
  mutate(Concept=as.factor(Concept)) %>% 
  mutate(Feature=as.factor(Feature))
```


## MERGE DATASETS

```{r}
library(fuzzyjoin)

# Perform fuzzy join to find common concepts
mcrae_concepts = mcrae_data_cleaned %>% select(Concept)

mcrae_data_cleaned_filtered = mcrae_data_cleaned %>% 
  mutate(Dataset = "MCRAE")

# Add dataset origin
mrngo_data_clened_metrics_richness_filtered <- mrngo_data_clened_metrics_richness %>%
  semi_join(mcrae_concepts, by = "Concept") %>%
  mutate(Dataset = "MRNGO")

# Stack datasets
mrngo_mcrae_merged <- bind_rows(mcrae_data_cleaned_filtered, mrngo_data_clened_metrics_richness_filtered)

# Reorder columns to place 'Dataset' first
mrngo_mcrae_merged <- mrngo_mcrae_merged %>% select(Dataset, everything())
  
```

```{r}
kremer_data_it = kremer_it_data_cleaned %>% 
  mutate(Dataset = "KREMER_IT")

kremer_data_de = kremer_de_data_cleaned %>% 
  mutate(Dataset = "KREMER_DE")

mrngo_data_clened_metrics_richness_filtered <- mrngo_data_clened_metrics_richness %>%
  semi_join(kremer_data_de, kremer_data_it, by = c("Concept", "Concept(EN)")) %>%
  mutate(Dataset = "MRNGO")

mrngo_kremer_merged <- bind_rows(kremer_data_de,kremer_data_it, mrngo_data_clened_metrics_richness_filtered)

mrngo_kremer_merged <- mrngo_kremer_merged %>% select(Dataset, everything())
```



## Demography

```{r}

mrngo_data_demography = mrngo_data_cleaned %>% 
  select(ID, sex, age) %>%  distinct()

# 1) Total counts by sex
mrngo_data_demography %>% 
  count(sex) %>% 
  rename(Count = n)

# 2) Summary of age (mean, median, SD, min, max)
mrngo_data_demography %>% 
  summarise(
    N         = n(),
    Mean_Age  = mean(age, na.rm = TRUE),
    Median_Age= median(age, na.rm = TRUE),
    SD_Age    = sd(age, na.rm = TRUE),
    Min_Age   = min(age, na.rm = TRUE),
    Max_Age   = max(age, na.rm = TRUE)
  )

# 3) Same summary broken down by sex
mrngo_data_demography %>% 
  group_by(sex) %>% 
  summarise(
    N         = n(),
    Mean_Age  = mean(age, na.rm = TRUE),
    Median_Age= median(age, na.rm = TRUE),
    SD_Age    = sd(age, na.rm = TRUE),
    Min_Age   = min(age, na.rm = TRUE),
    Max_Age   = max(age, na.rm = TRUE)
  )

# 4) Age distribution histogram by sex, with English labels and a caption
mrngo_data_demography %>% 
  ggplot(aes(x = age, fill = sex)) +
  geom_histogram(binwidth = 1, position = "dodge", color = "black") +
  labs(
    title   = "Age Distribution by Sex",
    x       = "Age (years)",
    y       = "Number of Participants",
    caption = "Figure: Histogram of participant ages, separated by sex"
  ) +
  theme_minimal()

# 5) Create age groups (6–8, 9–11, 12+) and summarize counts by group and sex
mrngo_data_demography2 <- mrngo_data_demography %>% 
  mutate(
    age_group = case_when(
      age <= 6            ~ "6",
      age <= 7           ~ "7",
      age <= 8                ~ "8",
      age <= 9                ~ "9"
    )
  )

mrngo_data_demography2 %>% 
  count(age_group, sex) %>% 
  tidyr::pivot_wider(
    names_from   = sex, 
    values_from  = n, 
    values_fill  = 0
  )


```

## Visualizations

### Response FREQ

```{r}

# 1) For each ID–concept, count the number of distinct features
id_concept_counts <- mrngo_data_cleaned %>% 
  distinct(ID, concept, feature) %>% 
  count(ID, concept, name = "n_features")

# 2) Now for each concept, compute descriptives across all IDs
concept_descriptives <- id_concept_counts %>% 
  group_by(ID) %>% 
  summarise(
    n_concepts        = n(),                # how many participants named that concept
    mean_feats   = mean(n_features),   # average features per participant
    median_feats = median(n_features),
    sd_feats     = sd(n_features),
    min_feats    = min(n_features),
    max_feats    = max(n_features)
  ) %>% 
  arrange(desc(mean_feats))

print(concept_descriptives)


```

```{r}
plot_freq = mrngo_data_cleaned %>% 
  # 1) dedupe feature-responses
  # 2) count how many features per (ID, concept)
  count(ID, concept, name = "n_features") %>% 
  # 3) average those counts *within* each ID
  group_by(ID) %>% 
  summarise(avg_response_rate = mean(n_features)) %>% 
  ungroup() %>% 
  # 4) histogram of the per-ID averages
  ggplot(aes(x = avg_response_rate)) +
    geom_histogram(binwidth = 1, colour = "white", fill = "#ccb3ff" ) +
    custom_theme +
    labs(x= "Average features produced by participants") +
    theme(
        axis.title.y = element_blank()
      ) 

print(plot_freq)

ggsave(
  filename = "../figures/avg_response_histogram.png",
  plot     = plot_freq,
  width    = 10,
  height   = 6,
  units    = "in",
  dpi      = 300
)
```

```{r}
mrngo_data_cleaned %>% 
  distinct(ID, concept, feature) %>% 
  count(ID, concept, name = "n_features") %>% 
  group_by(ID) %>% 
  summarise(avg_feats = mean(n_features)) %>% 
  ungroup() %>% 
  summarise(
    n_IDs        = n(),
    mean_of_means  = mean(avg_feats),
    median_of_means= median(avg_feats),
    sd_of_means    = sd(avg_feats),
    min_of_means   = min(avg_feats),
    max_of_means   = max(avg_feats)
  ) %>% 
  print()
```

### Feature FREQ

```{r}

feature_freq_plot = mrngo_data_cleaned %>% 
  count(feature, name = "n_features") %>% 
  arrange(desc(n_features)) %>%
  head(10) %>% 
  mutate(feature = fct_reorder(feature, n_features)) %>% 
  mutate(feature = recode(feature, !!!translations)) %>% 
  ggplot(aes(x = feature, y = n_features)) +
    geom_col(colour = "white", fill = "#ccb3ff") +
    coord_flip() +         # optional: flip for readability
    custom_theme +
    labs(x = NULL, y = NULL) + 
    theme(
      axis.text.y = element_text(hjust = 1)
    )

show(feature_freq_plot) 

ggsave(
  filename = "../figures/feature_frequency_count.png",
  plot     = feature_freq_plot,
  width    = 9,
  height   = 6,
  units    = "in",
  dpi      = 300
)

```

### CONCEPT DISTINCT

```{r}

mrngo_data_clened_metrics %>%
  # keep only distinguishing features
  filter(Disting == "D") %>%
  # count how many distinct features per concept
  distinct(concept, feature, .keep_all = TRUE) %>%
  count(concept, name = "n_dist_feats") %>%
  # take the top 10
  arrange(desc(n_dist_feats)) %>%
  slice_head(n = 10) %>%
  # make sure bars are ordered descending
  ggplot(aes(x = reorder(concept, n_dist_feats), y = n_dist_feats)) +
    geom_col(colour = "white", fill = "#ccb3ff") +
    custom_theme +
    labs(
      x = NULL,
      y = NULL
    ) +
    # rotate x labels so they fit
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )

richness_plot = mrngo_data_clened_metrics_richness %>% 
  distinct(concept, S_hat) %>% 
  arrange(desc(S_hat)) %>% 
  slice_head(n = 10) %>% 
  ggplot(aes(x = fct_reorder(concept, S_hat), y = S_hat)) +
    geom_col(fill = "#ccb3ff", colour = "white") +
    coord_flip() +
    custom_theme +
    labs(
      title = NULL,
      x     = NULL,
      y     = NULL
    )

show(richness_plot)

ggsave(
  filename = "../figures/feature_richness_count.png",
  plot     = richness_plot,
  width    = 9,
  height   = 6,
  units    = "in",
  dpi      = 300
)

```

### CORRELATION between stimuli metrics and richness

```{r}
library(ggpubr)
library(patchwork)  # for arranging multiple plots

# prepare your data (as before)
cmpl <- mrngo_data_clened_metrics_richness %>% 
  select(concept, S_hat, word_frequency, aoa_any) %>% 
  filter(!is.na(S_hat), !is.na(word_frequency), !is.na(aoa_any))

# Plot 1: Richness vs. Word Frequency
p1 <- cmpl %>%
  filter(S_hat != max(S_hat, na.rm = TRUE)) %>% 
  filter(S_hat != max(S_hat, na.rm = TRUE)) %>% 
  ggplot(aes(x = word_frequency, y = S_hat)) +
    geom_point(size = 2, alpha = 0.7) +
    geom_smooth(method = "lm", se = TRUE, color = "steelblue") +
    stat_cor(method = "pearson", label.x = Inf, label.y = Inf,
             hjust = 1.1, vjust = 1.5, size = 7) +
    labs(
      x     = "Word Frequency",
      y     = bquote("Semantic richness ("~hat(S)~")"),
      title = NULL
    ) +
  custom_theme

# Plot 2: Richness vs. Age-of‐Acquisition
p2 <- cmpl %>% 
  ggplot(aes(x = aoa_any, y = S_hat)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "coral") +
  stat_cor(method = "pearson", label.x = Inf, label.y = Inf,
           hjust = 1.1, vjust = 1.5, size = 7) +
  labs(
    x     = "Age of Acquisition (AoA)",
    y     = NULL,
    title = NULL
  ) +
  custom_theme

# Combine side by side
combined_plot <- p1 + p2 + 
  plot_layout(ncol = 2) & 
  theme(
    plot.title   = NULL,
    axis.text    = element_text(color = "gray30"),
    axis.title   = element_text(face = "bold")
  ) +
  custom_theme

# Print it (and you can ggsave at high‐res right after)
print(combined_plot)
print(p1)
print(p2)

ggsave(
  filename = "../figures/correlation_freq.png",
  plot     = p1,
  width    = 9,
  height   = 7,
  units    = "in",
  dpi      = 300
)


ggsave(
  filename = "../figures/correlation_aoa.png",
  plot     = p2,
  width    = 9,
  height   = 7,
  units    = "in",
  dpi      = 300
)

```

### PERFORMANCE BY GENDER \* AGE

```{r}

library(dplyr)
library(ggplot2)
library(ggpubr)

# 1) compute avg features-per-concept by ID
id_avg <- mrngo_data_cleaned %>% 
  distinct(ID, concept, feature) %>%     # one row per ID–concept–feature
  count(ID, concept, name = "n_feats") %>%  # how many features each ID gave for each concept
  group_by(ID) %>% 
  summarise(avg_feats = mean(n_feats, na.rm = TRUE)) %>% 
  ungroup()

# 2) pull out each ID’s age & sex (assumed unique per ID)
demog <- mrngo_data_cleaned %>% 
  select(ID, age, sex) %>% 
  distinct(ID, .keep_all = TRUE)

id_demo <- left_join(id_avg, demog, by = "ID")

id_demo_clean <- id_demo %>%
  mutate(
    age_f = factor(age, levels = sort(unique(age)))
  )

# 3) BAR + error‐bars (mean ± SE)
p3 <- ggplot(id_demo_clean, aes(x = age_f, y = avg_feats, fill = sex)) +
  stat_summary(
    fun = mean, geom = "col",
    position = position_dodge(width = 0.8),
    width = 0.6
  ) +
  stat_summary(
    fun.data = mean_se, geom = "errorbar",
    position = position_dodge(width = 0.8),
    width = 0.2
  ) +
  scale_fill_manual(values = c(female = "#F17C5D", male = "#5DA8D3")) +
  labs(
    x    = "Age",
    y    = "Avg. features per concept",
    fill = "Sex",
    title = NULL
  ) +
  custom_theme

# draw whichever you like:
print(p3)

ggsave(
  filename = "../figures/age_sex_difference.png",
  plot     = p3,
  width    = 10,
  height   = 6,
  units    = "in",
  dpi      = 300
)

```

## Analysis


### H1
mutate-tel a WB-s oszlopokat faktorrá kell alakítani,
ifelse változóval olyan oszlop, amiben a WB_Maj alapján kategorizálom hogy fankcionális-e vagy sem (0 ha nem, 1 ha igen)
summarise-olni kell a dataset-et úgy, hogy számolja meg azonosítónként (ID), hogy hány fuknciónális label van (count legyen a név mondjuk)
```{r}
mrngo_cleaned_h1 = mrngo_data_cleaned %>% 
  select(c("ID", "age", "sex", "feature", "category", "concept", "WB_label", "WB_Maj", "WB_Min")) %>% 
  mutate(above_seven = ifelse(age>7, 1, 0))

```

```{r}
t.test(count_h1, above_seven, data=mrngo_cleaned_h1)
```

### H2
utánanézni, hogy hogyan lehet egy "or" logikai tesztet csinálni az ifelse parancsban (WB_Maj == "c" vagy "e")
summarise-olni kell a dataset-et úgy, hogy számolja meg dataset-enként és conceptenként, hogy hány 1 label van (count legyen a név mondjuk)
```{r}
mrngo_cleaned_h2 = mrngo_mcrae_merged %>% 
  select(Dataset, Concept, WB_Maj) %>% 
  mutate() 
```
```{r}
t.test(count_h2, is_ce, data=mrngo_cleaned_h2)
```
### H3

```{r}
mrngo_cleaned_h3 = mrngo_data_clened_metrics_richness %>% 
  select(Concept, natural, S_hat) %>% 
  distinct()

t.test(S_hat ~ natural, data=mrngo_cleaned_h3)
```


### H4
```{r}
mrngo_data_h4 = 
```

### Correlations

```{r}

cmpl <- mrngo_data_clened_metrics_richness %>%
  select(concept, S_hat, word_frequency, aoa_any) %>%
  filter(!is.na(S_hat), !is.na(word_frequency), !is.na(aoa_any))

# 1) Richness vs. word_frequency
wf_ct  <- cor.test(cmpl$S_hat, cmpl$word_frequency, 
                   method = "pearson", 
                   use    = "complete.obs")

# 2) Richness vs. aoao_any
aoa_ct <- cor.test(cmpl$S_hat, cmpl$aoa_any, 
                   method = "pearson", 
                   use    = "complete.obs")

# Print your results
wf_ct
aoa_ct

# If you just want the raw r‐values:
data.frame(
  cor_richness__wf  = wf_ct$estimate,
  cor_richness__aoa = aoa_ct$estimate
)

```

### ANOVA - feature count

```{r}

# 1) Fit the ANOVA model
anova_mod <- aov(avg_feats ~ age * sex, data = id_demo)

# 2) Get the ANOVA table
anova_res <- summary(anova_mod)
print(anova_res)


```

### WordAnalytics

```{r}

WordListsAnalytics()


```
